\label{ch:background}

In order to define a common ground for the reader, this chapter introduces the main contents on which this work is based. For this purpose, a brief introduction about the current \textbf{state of knowledge} in terms of fall detection and the role of the \textbf{Electrodermal Activity} is proposed. Additionally, the concept of \textbf{Wearable Device} is briefly introduced.

% TODO evaluate the title, might need to be changed
\section{Benefits and Progress of Fall Detection Systems }\label{sec:fallintro}

% file:///Users/andrea/Downloads/sensors-21-05134-v2.pdf
In the field of research, a fall is described as an \textbf{unpredicted event} leading a subject to rest on the floor level~\cite{Lamb1}. On that basis, the activity of Fall Detection has referred to the identification of a fall through sensors and cameras in order to request assistance.

Over the past twenty years, researchers from all over the world worked on data retrieved from individual sources (such as gyroscopes and accelerometers) at the beginning and subsequently started investigating a \textbf{fusion based approach}. This involves the collection of multiple data of various nature and lead to more robust and increasingly accurate classification models. 

Vision based approaches gained importance over the last decade, thanks to the improvements in the world of \textbf{Machine vision} and to new technologies such as \textbf{depth cameras} \cite{elderlySurvey}. Major advancements in fall detection systems have, in fact, been reached by leveraging both vision and sensor-fusion based solutions. 

This latter approach gives rise to various difficulties in terms of data retrieval, synchronization, storage, processing and analysis, which may be overcome thanks to the continuous advancements in technology.

% Furthermore, various classifications of falls have been outlined. An accurate set of categories was described by Chan \textit{et al., 2018}~\cite{Chen1}, whose study about the specifications of built-in accelerometers in smartphones on fall detection performance divides falls in the following categories: 

% \begin{itemize}
%     \item Fall lateral left and lie on the floor
%     \item Fall lateral left and sit up from the floor
%     \item Fall lateral right and lie on the floor
%     \item Fall lateral right and sit up from the floor
%     \item Fall forward and lie on the floor
%     \item Fall backward and lie on the floor
% \end{itemize}

Researchers had also pointed out other important aspects that should be considered, such as a complete and detailed classifications of various kind of falls (in order to acquire different sets of information), their duration, the age and gender of the individual, together with its \textbf{mental} and \textbf{physical} condition.
Because most of the research conducted does not consider all these aspects together, the models obtained tend not to generalize well in real-life situations, leading to \textbf{inaccuracy}.

On this purpose, data retrieved from biosensors may be evaluated in order to provide information regarding an individual's condition in the context of a fall.

\section{The Autonomic Nervous System Activity}\label{sec:edaintro}

The \textbf{Autonomic Nervous System} constitutes an essential component of the peripheral nervous system aimed at controlling smooth muscles and glands functionality in the human body \cite{ansWiki}.

The three branches that compose the autonomic nervous system are:

\begin{itemize}
    \item \textbf{Sympathetic nervous system} (responsible for stimulating the \textit{fight or flight} response, which prepares the organism to address situations of danger or emotional distress)
    \item \textbf{Parasympathetic nervous system} (responsible for regulating unsconscious actions of the organism)
    \item \textbf{Enteric nervous system} (responsible for the Nervous Activity in the digestive system)
\end{itemize}

The activity of sweat glands endures a variation directly proportional to the activity of the sympathetic nervous system. On this purpose, analyzing the various changes in the sweat glands activity constitutes a valid criteria to depict the behaviour of the sympathetic nervous system and its reponse to external stimuli.


