\label{ch:collection}

%               ROADMAP
% =====================================
%
% we decided to use a commercial product
% movisens and the edamove4
%     - movisens
%     - edamove4
%     - sensor usage and data retrieval
%     - accessory tools
%     - unisens data format
%     - data analyzer and implemented features
% data Collection (falls performed and the hospital context)
% results
%

In order to further investigate the result obtained during the first experimentation session, a second testing trial was performed. This allowed the collection of additional data in order to draw conclusions in relation to the \textbf{feasibility} of the Electrodermal Activity analysis for classification purposes in the context of fall detection.

In this case, a commercial and publicly acknowledged device was employed in order to overcome the issues concerning the sensitivity to shocks and impacts of the BITalino device and, in addition, to acquire further bio-signals along with the Electrodermal Activity data.

\section{Movisens GmbH and the EdaMove Sensor}\label{sec:movisens}

The device employed consists of the \textbf{EdaMove4} sensor by \textbf{Movisens GmbH}, which is one of the most accurate and popular wearable devices aimed at the Electrodermal Activity measurement together with other such as the previously mentioned \textbf{Empatica E4}. Therefore, the following sections propose a brief overview of the product and its features.

\subsection{The company}\label{subsec:movisens-company}


Movisens GmbH is a German company deemed as a global leader in ambulatory assessment solutions \cite{movisens}, which offers several services such as workshops, consults, customized products and software in order to both support researchers and provide technologies and solutions for the healthcare sector.
The current catalog offers several sensor units for data collection and different mobile and desktop applications for data integration, processing and analysis. More specifically, the table \ref{toc:movisens-products} provides a list of the current available products.

\begin{table}[H]
\centering
\begin{tabular}{ll}
    \hline
    Name                     &  Description \\
    \hline
    \textbf{Move 4}          & A 10-Axis IMU that integrates a temperature sensor \\
    \textbf{EcgMove 4}       & A Move 4 unit that integrates ECG data collection  \\
    \textbf{EdaMove 4}       & A Move 4 unit that integrates EDA data collection \\
    \textbf{LightMove 4}     & A Move 4 unit that integrates the acquisition of ambient light measurements \\
    \textbf{SensorTrigger}   & A mobile solutions for activity-triggered data logging \\
    \textbf{movisensXS}      & A mobile solutions for Experience Sampling purposes \\
    \textbf{DataMerger}      & A desktop-based application for the integration of heterogeneous data \\
    \textbf{DataAnalyzer}    & A desktop-based application to analyze and report the acquired data \\
    \textbf{Unisens Viewer}  & A desktop-based application to examine the acquire data \\
    \hline
\end{tabular}
\caption{List of products offered by Movisens GmbH}
\label{toc:movisens-products}
\end{table}

Moreover, the company provides several solutions that allow researchers and students to utilize the needed instrumentation by requiring a free, limited rent for a specific product. In this case, the company has consented a rental related to the \textbf{EdaMove 4} sensor for the required period of time. 

\subsection{The EdaMove 4 Sensor}\label{subsec:edamove4}



